Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-12 ms.tex
Removed todo: don't need citation for training time of logistic regression as a function of C_{LogReg}.

In practice, there is something of a trade-off between accuracy and
computational resources because a larger value of $C_\text{LogReg}$
will also increase the training time, since a larger $C_\text{LogReg}$
corresponds to a less constrained parameter space being searched
\todo{(citation needed)}.
We discuss the performance and training time dependence on $C_\text{LogReg}$
in Section\ref{sec:regularization}.

>>>>

In practice, there is something of a trade-off between accuracy and
computational resources because a larger value of $C_\text{LogReg}$
will also increase the training time, since a larger $C_\text{LogReg}$
corresponds to a less constrained parameter space being searched.
We discuss the performance and training time dependence on $C_\text{LogReg}$
in Section\ref{sec:regularization}.
